---
title: "Alcohol vs Seat choice"
author: "La Kayla Thompson"
date: "Summer 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```

# Introduction
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

The data came from UCDavis in the year 2015.

$H_0$: There is no difference between the average number of drinks imbibed between people conditioned on the row they sit in.

$H_A$: The average number drinks is different between at least two rows.

# Methods

In the data set davisdata Seat is a categorical variable, alcohol is a numerical

We try to predict alcohol ~ Seat so we use the Numerical~Cat helper file

# Results

## Descriptive Results

### Graphical Summary

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```

Now add in boxplot

```{r}
basicCN + geom_boxplot()
```

This boxplot shows that the back seat has the highest variation in alcohol levels, while the front seat has the least.

### Numerical Summary

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

The numerical summary shows:

In the back seats, alcohol range is from 0 to 55, with a common value of 3.5 and an average of 8.56. 

In the front seats, alcohol levels range from 0 to 20 , with a common value of 0 and an average of 1.79.

In the middle seats, alcohol levels range from 0 to 35, with a common value of 1 and an average of 3.33.


### Inferential Results

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
The p-value is 0.000116, less than 0.005 so we reject the null hypothesis.
There is a difference in alcohol consumption based on where people sit.

## When significant follow up with TukeyHSD  

```{r}
plot(TukeyHSD(model1))
```
The turkey plot shows that the chances of the middle-front seats have a low probability of the alcohol levels than the front-back seats, as they fall in between 0.

## Conclusions

The seats in the back have a higher average of people consuming alcohol than those in the front or middle seats. Since the p-value is 0.000116, less than 0.005 so we reject the null hypothesis. The turkey plot shows that there is a difference in alcohol consumption based on where people sit.
